---
title: "Univariate Analysis"
author: "Katie Murphy"
date: "27/02/2021"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
rm(list=ls())
library(readxl)
library(dplyr)

for(i in 1:6){
    r <- assign(paste0("r",i), (as.data.frame(read_excel("C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/survey responses/raw.xlsx", paste0("R - v",i)))))
    py <- assign(paste0("py",i), (as.data.frame(read_excel("C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/survey responses/raw.xlsx", paste0("Py - v",i)))))
    assign(paste0("ver",i), rbind(r, py))
}

ver1 <- ver1[-1,]
r1 <- r1[-1,]
py1 <- py1[-1,]

names(ver1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )

names(r1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )

names(py1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )

names(r2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )

names(py2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )

names(r3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )

names(py3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )
###

names(ver4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )

names(r4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )

names(py4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(r5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(py5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )
###

names(ver6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )
                 
names(r6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(py6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )
### Y SCALES 
ctrl_y_scale <- rbind(ver1[,c(4:7, 10:13)], ver2[,c(4:7, 10:13)], ver3[,c(4:7, 14:17)], ver4[,c(4:7, 18:21)], ver5[,c(4:7, 14:17)], ver6[,c(4:7, 18:21)])
log_y_scale <- rbind(ver1[,c(4:7, 14:17)], ver2[,c(4:7, 18:21)], ver3[,c(4:7, 10:13)], ver4[,c(4:7, 10:13)], ver5[,c(4:7, 18:21)], ver6[,c(4:7, 14:17)])
trnc_y_scale <- rbind(ver1[,c(4:7, 18:21)], ver2[,c(4:7, 14:17)], ver3[,c(4:7, 18:21)], ver4[,c(4:7, 14:17)], ver5[,c(4:7, 10:13)], ver6[,c(4:7, 10:13)])
```
# Y scales

#### *Q1 - Approximately many times would you say the 'Salmon Ladder' was used?*
# Both
#### Both - all
```{r echo=F}
con_1_all <- ctrl_y_scale$con_1
con_1_all[26] <- 41.5 # take midpoint of two values
con_1_all <- as.numeric(con_1_all)

trn_1_all <- as.numeric(trnc_y_scale$trn_1)

log_1_all <- log_y_scale$log_1
log_1_all[which(log_1_all == "Don't know")] <- NA
log_1_all[which(log_1_all == "Next to none.")] <- NA
log_1_all[which(log_1_all == "10^15")] <- 1e+15
log_1_all[which(log_1_all == "10^9")] <- 1e+9
log_1_all <- as.numeric(log_1_all)

y_scale_1_all <- cbind(con_1_all, trn_1_all, log_1_all)
summary(y_scale_1_all)
noquote(paste0("NA at index ", which(is.na(y_scale_1_all)), "."))
```

#### Both - degree
```{r echo=F}

deg_codes <- c("mat", "sci", "arts", "soc_sci", "eng", "arch", "bus", "tech", "NA", "med", "hum", "crim", "psych", "geog", "sus")

for(i in 1:length(unique(ctrl_y_scale$uni))){
  assign(paste0(deg_codes[i],"_crtl"), ctrl_y_scale %>% filter(uni == unique(ctrl_y_scale$uni)[i]))
}

for(i in 1:length(unique(trnc_y_scale$uni))){
  assign(paste0(deg_codes[i],"_trnc"), trnc_y_scale %>% filter(uni == unique(trnc_y_scale$uni)[i]))
}

for(i in 1:length(unique(log_y_scale$uni))){
  assign(paste0(deg_codes[i],"_log"), log_y_scale %>% filter(uni == unique(log_y_scale$uni)[i]))
}

```



##### Science
```{r echo=F}
con_1 <- as.numeric(sci_crtl$con_1)
log_1 <- as.numeric(sci_log$log_1) 
trn_1 <- as.numeric(sci_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Technology
```{r echo=F}
con_1 <- as.numeric(tech_crtl$con_1)
log_1 <- as.numeric(tech_log$log_1) 
trn_1 <- as.numeric(tech_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))

#NA: 'Don't know'
```
##### Engineering
```{r echo=F}
con_1 <- as.numeric(eng_crtl$con_1)
log_1 <- as.numeric(eng_log$log_1) 
trn_1 <- as.numeric(eng_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Maths
```{r echo=F}
con_1 <- as.numeric(mat_crtl$con_1)
log_1 <- as.numeric(mat_log$log_1) 
trn_1 <- as.numeric(mat_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```

##### Arts
```{r echo=F}
con_1 <- as.numeric(arts_crtl$con_1)
log_1 <- as.numeric(arts_log$log_1) 
trn_1 <- as.numeric(arts_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Social sciences
```{r echo=F}
con_1 <- as.numeric(c(soc_sci_crtl$con_1, psych_crtl$con_1))

log_1 <- c(soc_sci_log$log_1, psych_log$log_1)
log_1 [which(log_1 == "10^15")] <- 1e+15
log_1 [which(log_1 == "10^9")] <- 1e+9
log_1  <- as.numeric(log_1)

trn_1 <- as.numeric(c(soc_sci_trnc$trn_1, psych_trnc$trn_1))

summary(cbind(con_1, log_1, trn_1))

```
##### Architecture
```{r echo=F}
con_1 <- as.numeric(arch_crtl$con_1)
log_1 <- as.numeric(arch_log$log_1) 
trn_1 <- as.numeric(arch_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Business
```{r echo=F}
con_1 <- as.numeric(bus_crtl$con_1)
log_1 <- as.numeric(bus_log$log_1) 
trn_1 <- as.numeric(bus_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Medicine
```{r echo=F}
con_1 <- as.numeric(med_crtl$con_1)
log_1 <- as.numeric(med_log$log_1) 
trn_1 <- as.numeric(med_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Humanities
```{r echo=F}
con_1 <- as.numeric(hum_crtl$con_1)
log_1 <- as.numeric(hum_log$log_1) 
trn_1 <- as.numeric(hum_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Criminology
```{r echo=F}
con_1 <- as.numeric(crim_crtl$con_1)
log_1 <- as.numeric(crim_log$log_1) 
trn_1 <- as.numeric(crim_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Geography
```{r echo=F}
con_1 <- as.numeric(geog_crtl$con_1)
log_1 <- as.numeric(geog_log$log_1) 
trn_1 <- as.numeric(geog_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```
##### Sustainability/geological science
```{r echo=F}
con_1 <- as.numeric(sus_crtl$con_1)
log_1 <- as.numeric(sus_log$log_1) 
trn_1 <- as.numeric(sus_trnc$trn_1)
summary(cbind(con_1, log_1, trn_1))
```

#### Both - v1 (CLT)
```{r echo=F}
CLT <- cbind(ver1[10], ver1[14], ver1[18])
summary(CLT)
```
#### Both - v2 (CTL)
```{r echo=F}
CTL <- cbind(ver2[10], ver2[18], ver2[14])
CTL[c(10, 12), 2] <- NA
CTL$log_1 <- as.numeric(CTL$log_1)
summary(CTL)
```
#### Both - v3 (LCT)
```{r echo=F}
LCT <- cbind(ver3[14], ver3[10], ver3[18])
LCT[1, 1] <- 41.5
LCT[10, 2] <- 1e+15

LCT$con_1 <- as.numeric(LCT$con_1)
LCT$log_1 <- as.numeric(LCT$log_1)

summary(LCT)
```
#### Both - v4 (LTC)
```{r echo=F}
LTC <- cbind(ver4[18], ver4[10], ver4[14])
summary(LTC)
```
#### Both - v5 (TCL)
```{r echo=F}
TCL <- cbind(ver5[14], ver5[18], ver5[10])
TCL[8, 2] <- 1e+9
TCL$log_1 <- as.numeric(TCL$log_1)

summary(TCL)
```
#### Both - v6 (TLC)
```{r echo=F}
TLC <- cbind(ver6[18], ver6[14], ver6[10])
summary(TLC)
```

# R
#### R - all
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,c(4:7, 10:13)], r2[,c(4:7, 10:13)], r3[,c(4:7, 14:17)], r4[,c(4:7, 18:21)], r5[,c(4:7, 14:17)], r6[,c(4:7, 18:21)])
log_y_scale_r <- rbind(r1[,c(4:7, 14:17)], r2[,c(4:7, 18:21)], r3[,c(4:7, 10:13)], r4[,c(4:7, 10:13)], r5[,c(4:7, 18:21)], r6[,c(4:7, 14:17)])
trnc_y_scale_r <- rbind(r1[,c(4:7, 18:21)], r2[,c(4:7, 14:17)], r3[,c(4:7, 18:21)], r4[,c(4:7, 14:17)], r5[,c(4:7, 10:13)], r6[,c(4:7, 10:13)])

con_1_r <- ctrl_y_scale_r$con_2
con_1_r[15] <- 41.5 # take midpoint of two values
con_1_r <- as.numeric(con_1_r)

trn_1_r <- as.numeric(trnc_y_scale_r$trn_2)

log_1_r <- log_y_scale_r$log_2

y_scale_r <- cbind(con_1_r, log_1_r, trn_1_r)
summary(y_scale_r)
```

```{r echo=F}

deg_codes <- c("mat", "sci", "arts", "soc_sci", "eng", "arch", "med", "tech", "bus", "crim", "hum", "geog")

for(i in 1:length(unique(ctrl_y_scale_r$uni))){
  assign(paste0(deg_codes[i],"_ctrl_r"), ctrl_y_scale_r %>% filter(uni == unique(ctrl_y_scale_r$uni)[i]))
}

for(i in 1:length(unique(trnc_y_scale_r$uni))){
  assign(paste0(deg_codes[i],"_trnc_r"), trnc_y_scale_r %>% filter(uni == unique(trnc_y_scale_r$uni)[i]))
}

for(i in 1:length(unique(log_y_scale_r$uni))){
  assign(paste0(deg_codes[i],"_log_r"), log_y_scale_r %>% filter(uni == unique(log_y_scale_r$uni)[i]))
}

```


##### Science
```{r echo=F}
con_1_r <- as.numeric(sci_ctrl_r$con_1)
log_1_r  <- as.numeric(sci_log_r$log_1) 
trn_1_r  <- as.numeric(sci_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r))
```
##### Technology
```{r echo=F}
con_1_r <- as.numeric(tech_ctrl_r$con_1)
log_1_r  <- as.numeric(tech_log_r$log_1) 
trn_1_r  <- as.numeric(tech_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))

```
##### Engineering
```{r echo=F}
con_1_r <- as.numeric(eng_ctrl_r$con_1)
log_1_r  <- as.numeric(eng_log_r$log_1) 
trn_1_r  <- as.numeric(eng_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r))
```
##### Maths
```{r echo=F}
con_1_r <- as.numeric(mat_ctrl_r$con_1)
log_1_r  <- as.numeric(mat_log_r$log_1) 
trn_1_r  <- as.numeric(mat_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```

##### Arts
```{r echo=F}
con_1_r <- as.numeric(arts_ctrl_r$con_1)
log_1_r  <- as.numeric(arts_log_r$log_1) 
trn_1_r  <- as.numeric(arts_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```
##### Social sciences
```{r echo=F}
con_1_r <- soc_sci_ctrl_r$con_1
con_1_r[which(con_1_r == "41/42")] <- 41.5
con_1_r <- as.numeric(con_1_r)

log_1_r  <- (soc_sci_log_r$log_1)

trn_1_r  <- as.numeric(soc_sci_trnc_r$trn_1)

summary(cbind(con_1_r, log_1_r , trn_1_r))

```
##### Architecture
```{r echo=F}
con_1_r <- as.numeric(arch_ctrl_r$con_1)
log_1_r  <- as.numeric(arch_log_r$log_1) 
trn_1_r  <- as.numeric(arch_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```
##### Business
```{r echo=F}
con_1_r <- as.numeric(bus_ctrl_r$con_1)
log_1_r  <- as.numeric(bus_log_r$log_1) 
trn_1_r  <- as.numeric(bus_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```
##### Medicine
```{r echo=F}
con_1_r <- as.numeric(med_ctrl_r$con_1)
log_1_r  <- as.numeric(med_log_r$log_1) 
trn_1_r  <- as.numeric(med_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```
##### Humanities
```{r echo=F}
con_1_r <- as.numeric(hum_ctrl_r$con_1)
log_1_r  <- as.numeric(hum_log_r$log_1) 
trn_1_r  <- as.numeric(hum_trnc_r$trn_1)
summary(cbind(con_1, log_1_r , trn_1))
```
##### Criminology
```{r echo=F}
con_1_r <- as.numeric(crim_ctrl_r$con_1)
log_1_r  <- as.numeric(crim_log_r$log_1) 
trn_1_r  <- as.numeric(crim_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```
##### Geography
```{r echo=F}
con_1_r <- as.numeric(geog_ctrl_r$con_1)
log_1_r  <- as.numeric(geog_log_r$log_1) 
trn_1_r  <- as.numeric(geog_trnc_r$trn_1)
summary(cbind(con_1_r, log_1_r , trn_1_r ))
```

#### R - v1 (CLT)
```{r echo=F}
CLT <- cbind(r1[10], r1[14], r1[18])
summary(CLT)
```
#### R - v2 (CTL)
```{r echo=F}
CTL <- cbind(r2[10], r2[18], r2[14])
summary(CTL)
```
#### R - v3 (LCT)
```{r echo=F}
LCT <- cbind(r3[14], r3[10], r3[18])
LCT[1, 1] <- 41.5
LCT$con_1 <- as.numeric(LCT$con_1)
summary(LCT)
```
#### R - v4 (LTC)
```{r echo=F}
LTC <- cbind(r4[18], r4[10], r4[14])
summary(LTC)
```
#### R - v5  (TCL)
```{r echo=F}
TCL <- cbind(r5[14], r5[18], r5[10])
summary(TCL)
```
#### R - v6 (TLC)
```{r echo=F}
TLC <- cbind(r6[18], r6[14], r6[10])
summary(TLC)
```

# Python
#### Python - all
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,c(4:7, 10:13)], py2[,c(4:7, 10:13)], py3[,c(4:7, 14:17)], py4[,c(4:7, 18:21)], py5[,c(4:7, 14:17)], py6[,c(4:7, 18:21)])
log_y_scale_py <- rbind(py1[,c(4:7, 14:17)], py2[,c(4:7, 18:21)], py3[,c(4:7, 10:13)], py4[,c(4:7, 10:13)], py5[,c(4:7, 18:21)], py6[,c(4:7, 14:17)])
trnc_y_scale_py <- rbind(py1[,c(4:7, 18:21)], py2[,c(4:7, 14:17)], py3[,c(4:7, 18:21)], py4[,c(4:7, 14:17)], py5[,c(4:7, 10:13)], py6[,c(4:7, 10:13)])

con_1_py <- ctrl_y_scale_py$con_1

trn_1_py <- as.numeric(trnc_y_scale_py$trn_1)

log_1_py <- log_y_scale_py$log_1
log_1_py[which(log_1_py == "Don't know")] <- NA
log_1_py[which(log_1_py == "Next to none.")] <- NA
log_1_py[which(log_1_py == "10^15")] <- 1e+15
log_1_py[which(log_1_py == "10^9")] <- 1e+9
log_1_py <- as.numeric(log_1_py)


y_scale_py <- cbind(con_1_py, log_1_py, trn_1_py)
summary(y_scale_py)
```

```{r echo=F}

deg_codes <- c("soc_sci", "sci", "bus", "tech", "NA", "mat", "eng", "hum", "psych", "sus")

for(i in 1:length(unique(ctrl_y_scale_py$uni))){
  assign(paste0(deg_codes[i],"_ctrl_py"), ctrl_y_scale_py %>% filter(uni == unique(ctrl_y_scale_py$uni)[i]))
}

for(i in 1:length(unique(trnc_y_scale_py$uni))){
  assign(paste0(deg_codes[i],"_trnc_py"), trnc_y_scale_py %>% filter(uni == unique(trnc_y_scale_py$uni)[i]))
}

for(i in 1:length(unique(log_y_scale_py$uni))){
  assign(paste0(deg_codes[i],"_log_py"), log_y_scale_py %>% filter(uni == unique(log_y_scale_py$uni)[i]))
}

```


##### Science
```{r echo=F}
con_1_py <- as.numeric(sci_ctrl_py$con_1)
log_1_py  <- as.numeric(sci_log_py$log_1) 
trn_1_py  <- as.numeric(sci_trnc_py$trn_1)
summary(cbind(con_1_py, log_1_py , trn_1_py))
```
##### Technology
##### NOTE: Only one respondent here, and they wrote 'Don't Know' for the log scale
```{r echo=F}
con_1_py <- as.numeric(tech_ctrl_py$con_1)
trn_1_py  <- as.numeric(tech_trnc_py$trn_1)
summary(cbind(con_1_py, trn_1_py ))
#NA: 'Don't know'
```
##### Engineering
```{r echo=F}
con_1_py <- as.numeric(eng_ctrl_py$con_1)
log_1_py  <- as.numeric(eng_log_py$log_1) 
trn_1_py  <- as.numeric(eng_trnc_py$trn_1)
summary(cbind(con_1_py, log_1_py , trn_1_py))
```
##### Maths
```{r echo=F}
con_1_py <- as.numeric(mat_ctrl_py$con_1)
log_1_py  <- as.numeric(mat_log_py$log_1) 
trn_1_py  <- as.numeric(mat_trnc_py$trn_1)
summary(cbind(con_1_py, log_1_py , trn_1_py ))
```

##### Social sciences
```{r echo=F}

con_1_py <- as.numeric(c(soc_sci_ctrl_py$con_1, psych_ctrl_py$con_1))

log_1_py <- c(soc_sci_log_py$log_1, psych_log_py$log_1)
log_1_py[which(log_1_py == "10^15")] <- 1e+15
log_1_py[which(log_1_py == "10^9")] <- 1e+9
log_1_py <- as.numeric(log_1_py)

trn_1_py <- as.numeric(c(soc_sci_trnc_py$trn_1, psych_trnc_py$trn_1))

summary(cbind(con_1_py, log_1_py , trn_1_py))

```
##### Business
```{r echo=F}
con_1_py <- as.numeric(bus_ctrl_py$con_1)
log_1_py  <- as.numeric(bus_log_py$log_1) 
trn_1_py  <- as.numeric(bus_trnc_py$trn_1)
summary(cbind(con_1_py, log_1_py , trn_1_py ))
```
##### Humanities
```{r echo=F}
con_1_py <- as.numeric(hum_ctrl_py$con_1)
log_1_py  <- as.numeric(hum_log_py$log_1) 
trn_1_py  <- as.numeric(hum_trnc_py$trn_1)
summary(cbind(con_1, log_1_py , trn_1))
```



#### Py - v1 (CLT)
```{r echo=F}
CLT <- cbind(py1[10], py1[14], py1[18])
summary(CLT)
```
#### Py - v2 (CTL)
```{r echo=F}
CTL <- cbind(py2[10], py2[18], py2[14])
CTL[c(4, 6), 2] <- NA
CTL$log_1 <- as.numeric(CTL$log_1)
summary(CTL)
```
#### Py - v3 (LCT)
```{r echo=F}
LCT <- cbind(py3[14], py3[10], py3[18])
LCT[5, 2] <- 1e+15
LCT$log_1 <- as.numeric(LCT$log_1)
summary(LCT)
```
#### Py - v4 (LTC)
```{r echo=F}
LTC <- cbind(py4[18], py4[10], py4[14])
summary(LTC)
```
#### Py - v5 (TCL)
```{r echo=F}
TCL <- cbind(py5[14], py5[18], py5[10])
TCL[3, 2] <- 1e+9
TCL$log_1 <- as.numeric(TCL$log_1)
summary(TCL)
```
#### Py - v6 (TLC)
```{r echo=F}
TLC <- cbind(py6[18], py6[14], py6[10])
summary(TLC)
```


#### *Q2 - Approximately how much more than 'Log Grip' would you say 'Salmon Ladder' was was used?*
# Both
#### Both - all
```{r echo=F}
con_2_all <- ctrl_y_scale[,2]
trn_2_all <- trnc_y_scale[,2]
log_2_all <- log_y_scale[,2]

y_scale_2_all <- cbind(con_2_all, log_2_all, trn_2_all)
summary(y_scale_2_all)
```

#### Both - v1 (CLT)
```{r echo=F}
CLT <- cbind(ver1[11], ver1[15], ver1[19])
summary(CLT)
```
#### Both - v2 (CTL)
```{r echo=F}
CTL <- cbind(ver2[11], ver2[19], ver2[15])
summary(CTL)
```
#### Both - v3 (LCT)
```{r echo=F}
LCT <- cbind(ver3[15], ver3[11], ver3[19])
summary(LCT)
```
#### Both - v4 (LTC)
```{r echo=F}
LTC <- cbind(ver4[19], ver4[11], ver4[15])
summary(LTC)
```
#### Both - v5 (TCL)
```{r echo=F}
TCL <- cbind(ver5[15], ver5[19], ver5[11])
summary(TCL)
```
#### Both - v6 (TLC)
```{r echo=F}
TLC <- cbind(ver6[19], ver6[15], ver6[11])
summary(TLC)
```

# R
#### R - all
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,c(4:7, 10:13)], r2[,c(4:7, 10:13)], r3[,c(4:7, 14:17)], r4[,c(4:7, 18:21)], r5[,c(4:7, 14:17)], r6[,c(4:7, 18:21)])
log_y_scale_r <- rbind(r1[,c(4:7, 14:17)], r2[,c(4:7, 18:21)], r3[,c(4:7, 10:13)], r4[,c(4:7, 10:13)], r5[,c(4:7, 18:21)], r6[,c(4:7, 14:17)])
trnc_y_scale_r <- rbind(r1[,c(4:7, 18:21)], r2[,c(4:7, 14:17)], r3[,c(4:7, 18:21)], r4[,c(4:7, 14:17)], r5[,c(4:7, 10:13)], r6[,c(4:7, 10:13)])

con_2_r <- ctrl_y_scale_r[,2]
trn_2_r <- trnc_y_scale_r[,2]
log_2_r <- log_y_scale_r[,2]

y_scale_2_r <- cbind(con_2_r, log_2_r, trn_2_r)
summary(y_scale_2_r)
```

#### R - v1 (CLT)
```{r echo=F}
CLT <- cbind(r1[11], r1[15], r1[19])
summary(CLT)
```
#### R - v2 (CTL)
```{r echo=F}
CTL <- cbind(r2[11], r2[19], r2[15])
summary(CTL)
```
#### R - v3 (LCT)
```{r echo=F}
LCT <- cbind(r3[15], r3[11], r3[19])
summary(LCT)
```
#### R - v4 (LTC)
```{r echo=F}
LTC <- cbind(r4[19], r4[11], r4[15])
summary(LTC)
```
#### R - v5 (TCL)
```{r echo=F}
TCL <- cbind(r5[15], r5[19], r5[11])
summary(TCL)
```
#### R - v6 (TLC)
```{r echo=F}
TLC <- cbind(r6[19], r6[15], r6[11])
summary(TLC)
```

# Python

#### Py - all
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,c(4:7, 10:13)], py2[,c(4:7, 10:13)], py3[,c(4:7, 14:17)], py4[,c(4:7, 18:21)], py5[,c(4:7, 14:17)], py6[,c(4:7, 18:21)])
log_y_scale_py <- rbind(py1[,c(4:7, 14:17)], py2[,c(4:7, 18:21)], py3[,c(4:7, 10:13)], py4[,c(4:7, 10:13)], py5[,c(4:7, 18:21)], py6[,c(4:7, 14:17)])
trnc_y_scale_py <- rbind(py1[,c(4:7, 18:21)], py2[,c(4:7, 14:17)], py3[,c(4:7, 18:21)], py4[,c(4:7, 14:17)], py5[,c(4:7, 10:13)], py6[,c(4:7, 10:13)])

con_2_py <- ctrl_y_scale_py[,2]
trn_2_py <- trnc_y_scale_py[,2]
log_2_py <- log_y_scale_py[,2]

y_scale_2_py <- cbind(con_2_py, log_2_py, trn_2_py)
summary(y_scale_2_py)
```

#### Py - v1 (CLT)
```{r echo=F}
CLT <- cbind(py1[11], py1[15], py1[19])
summary(CLT)
```
#### Py - v2 (CTL)
```{r echo=F}
CTL <- cbind(py2[11], py2[19], py2[15])
summary(CTL)
```
#### Py - v3 (LCT)
```{r echo=F}
LCT <- cbind(py3[15], py3[11], py3[19])
summary(LCT)
```
#### Py - v4 (LTC)
```{r echo=F}
LTC <- cbind(py4[19], py4[11], py4[15])
summary(LTC)
```
#### Py - v5 (TCL)
```{r echo=F}
TCL <- cbind(py5[15], py5[19], py5[11])
summary(TCL)
```
#### Py - v6 (TLC)
```{r echo=F}
TLC <- cbind(py6[19], py6[15], py6[11])
summary(TLC)
```





#### *Q3 - Approximately how much more than 'Quintuple Steps' would you say 'Salmon Ladder' was used?*
# Both
#### Both - all
```{r echo=F}
con_3_all <- ctrl_y_scale[,3]
trn_3_all <- trnc_y_scale[,3]
log_3_all <- log_y_scale[,3]

y_scale_3_all <- cbind(con_3_all, log_3_all, trn_3_all)
summary(y_scale_3_all)
```

#### Both - v1 (CLT)
```{r echo=F}
CLT <- cbind(ver1[12], ver1[16], ver1[20])
summary(CLT)
```
#### Both - v2 (CTL)
```{r echo=F}
CTL <- cbind(ver2[12], ver2[20], ver2[16])
summary(CTL)
```
#### Both - v3 (LCT)
```{r echo=F}
LCT <- cbind(ver3[16], ver3[12], ver3[20])
summary(LCT)
```
#### Both - v4 (LTC)
```{r echo=F}
LTC <- cbind(ver4[20], ver4[12], ver4[16])
summary(LTC)
```
#### Both - v5 (TCL)
```{r echo=F}
TCL <- cbind(ver5[16], ver5[20], ver5[12])
summary(TCL)
```
#### Both - v6 (TLC)
```{r echo=F}
TLC <- cbind(ver6[20], ver6[16], ver6[12])
summary(TLC)
```

# R
#### R - all
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,c(4:7, 10:13)], r2[,c(4:7, 10:13)], r3[,c(4:7, 14:17)], r4[,c(4:7, 18:21)], r5[,c(4:7, 14:17)], r6[,c(4:7, 18:21)])
log_y_scale_r <- rbind(r1[,c(4:7, 14:17)], r2[,c(4:7, 18:21)], r3[,c(4:7, 10:13)], r4[,c(4:7, 10:13)], r5[,c(4:7, 18:21)], r6[,c(4:7, 14:17)])
trnc_y_scale_r <- rbind(r1[,c(4:7, 18:21)], r2[,c(4:7, 14:17)], r3[,c(4:7, 18:21)], r4[,c(4:7, 14:17)], r5[,c(4:7, 10:13)], r6[,c(4:7, 10:13)])

con_3_r <- ctrl_y_scale_r[,3]
trn_3_r <- trnc_y_scale_r[,3]
log_3_r <- log_y_scale_r[,3]

y_scale_3_r <- cbind(con_3_r, log_3_r, trn_3_r)
summary(y_scale_3_r)
```

#### R - v1 (CLT)
```{r echo=F}
CLT <- cbind(r1[12], r1[16], r1[20])
summary(CLT)
```
#### R - v2 (CTL)
```{r echo=F}
CTL <- cbind(r2[12], r2[20], r2[16])
summary(CTL)
```
#### R - v3 (LCT)
```{r echo=F}
LCT <- cbind(r3[16], r3[12], r3[20])
summary(LCT)
```
#### R - v4 (LTC)
```{r echo=F}
LTC <- cbind(r4[20], r4[12], r4[16])
summary(LTC)
```
#### R - v5 (TCL)
```{r echo=F}
TCL <- cbind(r5[16], r5[20], r5[12])
summary(TCL)
```
#### R - v6 (TLC)
```{r echo=F}
TLC <- cbind(r6[20], r6[16], r6[12])
summary(TLC)
```


#### Python
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,c(4:7, 10:13)], py2[,c(4:7, 10:13)], py3[,c(4:7, 14:17)], py4[,c(4:7, 18:21)], py5[,c(4:7, 14:17)], py6[,c(4:7, 18:21)])
log_y_scale_py <- rbind(py1[,c(4:7, 14:17)], py2[,c(4:7, 18:21)], py3[,c(4:7, 10:13)], py4[,c(4:7, 10:13)], py5[,c(4:7, 18:21)], py6[,c(4:7, 14:17)])
trnc_y_scale_py <- rbind(py1[,c(4:7, 18:21)], py2[,c(4:7, 14:17)], py3[,c(4:7, 18:21)], py4[,c(4:7, 14:17)], py5[,c(4:7, 10:13)], py6[,c(4:7, 10:13)])

con_3_py <- ctrl_y_scale_py[,3]
trn_3_py <- trnc_y_scale_py[,3]
log_3_py <- log_y_scale_py[,3]

y_scale_3_py <- cbind(con_3_py, log_3_py, trn_3_py)
summary(y_scale_3_py)
```


#### Py - v1 (CLT)
```{r echo=F}
CLT <- cbind(py1[12], py1[16], py1[20])
summary(CLT)
```
#### Py - v2 (CTL)
```{r echo=F}
CTL <- cbind(py2[12], py2[20], py2[16])
summary(CTL)
```
#### Py - v3 (LCT)
```{r echo=F}
LCT <- cbind(py3[16], py3[12], py3[20])
summary(LCT)
```
#### Py - v4 (LTC)
```{r echo=F}
LTC <- cbind(py4[20], py4[12], py4[16])
summary(LTC)
```
#### Py - v5 (TCL)
```{r echo=F}
TCL <- cbind(py5[16], py5[20], py5[12])
summary(TCL)
```
#### Py - v6 (TLC)
```{r echo=F}
TLC <- cbind(py6[20], py6[16], py6[12])
summary(TLC)
```



#### *Q4 - In your opinion, approximately how many times would you say 'Log Grip' was used, as a percentage of the number of times 'Salmon Ladder' was used?*

# Both
#### Both - all
```{r echo=F}
con_4_all <- ctrl_y_scale[,4]
con_4_all[18] <- 12.5
con_4_all <- as.numeric(con_4_all)
for(i in 1:length(con_4_all)){
    if(con_4_all[i] < 1 && is.na(con_4_all[i])==FALSE){
       con_4_all[i] <- con_4_all[i]*100
    }
}


trn_4_all <- trnc_y_scale[,4]
for(i in 1:length(trn_4_all)){
    if(trn_4_all[i] < 1 && is.na(trn_4_all[i])==FALSE){
       trn_4_all[i] <- trn_4_all[i]*100
    }
}

log_4_all <- log_y_scale[,4]
log_4_all[18] <- 3
log_4_all <- as.numeric(log_4_all)
trn_4_all <- trnc_y_scale[,4]
for(i in 1:length(log_4_all)){
    if(log_4_all[i] < 1 && is.na(log_4_all[i])==FALSE){
       log_4_all[i] <- log_4_all[i]*100
    }
}



y_scale_4_all <- cbind(con_4_all, log_4_all, trn_4_all)
summary(y_scale_4_all)
```

#### Both - Degree
```{r echo=F}


```

#### Both - v1 (CLT)
```{r echo=F}
CLT <- cbind(ver1[13], ver1[17], ver1[21])

for(i in 1:dim(CLT)[1]){
    if(CLT[i, 1] < 1 && is.na(CLT[i, 1])==FALSE){
       CLT[i, 1] <- CLT[i, 1]*100
    } 
  
    if(CLT[i, 2] < 1 && is.na(CLT[i, 2])==FALSE){
       CLT[i, 2] <- CLT[i, 2]*100
    }
  
    if(CLT[i, 3] < 1 && is.na(CLT[i, 3])==FALSE){
       CLT[i, 3] <- CLT[i, 3]*100
    }
}

summary(CLT)
```

#### Both - v2 (CTL)
```{r echo=F}
CTL <- cbind(ver2[13], ver2[21], ver2[17])
CTL$con_4[5] <- 12.5
CTL$log_4[5] <- 3

CTL$log_4 <- as.numeric(CTL$log_4)
CTL$con_4 <- as.numeric(CTL$con_4)

for(i in 1:dim(CTL)[1]){
    if(CTL[i, 1] < 1 && is.na(CTL[i, 1])==FALSE){
       CTL[i, 1] <- CTL[i, 1]*100
    } 
  
    if(CTL[i, 2] < 1 && is.na(CTL[i, 2])==FALSE){
       CTL[i, 2] <- CTL[i, 2]*100
    }
  
    if(CTL[i, 3] < 1 && is.na(CTL[i, 3])==FALSE){
       CTL[i, 3] <- CTL[i, 3]*100
    }
}


summary(CTL)
```
#### Both - v3 (LCT)
```{r echo=F}
LCT <- cbind(ver3[17], ver3[13], ver3[21])

for(i in 1:dim(LCT)[1]){
    if(LCT[i, 1] < 1 && is.na(LCT[i, 1])==FALSE){
       LCT[i, 1] <- LCT[i, 1]*100
    } 
  
    if(LCT[i, 2] < 1 && is.na(LCT[i, 2])==FALSE){
       LCT[i, 2] <- LCT[i, 2]*100
    }
  
    if(LCT[i, 3] < 1 && is.na(LCT[i, 3])==FALSE){
       LCT[i, 3] <- LCT[i, 3]*100
    }
}

summary(LCT)
```
#### Both - v4 (LTC)
```{r echo=F}
LTC <- cbind(ver4[21], ver4[13], ver4[17])

for(i in 1:dim(LTC)[1]){
    if(LTC[i, 1] < 1 && is.na(LTC[i, 1])==FALSE){
       LTC[i, 1] <- LTC[i, 1]*100
    } 
  
    if(LTC[i, 2] < 1 && is.na(LTC[i, 2])==FALSE){
       LTC[i, 2] <- LTC[i, 2]*100
    }
  
    if(LTC[i, 3] < 1 && is.na(LTC[i, 3])==FALSE){
       LTC[i, 3] <- LTC[i, 3]*100
    }
}

summary(LTC)
```
#### Both - v5 (TCL)
```{r echo=F}
TCL <- cbind(ver5[17], ver5[21], ver5[13])

for(i in 1:dim(TCL)[1]){
    if(TCL[i, 1] < 1 && is.na(TCL[i, 1])==FALSE){
       TCL[i, 1] <- TCL[i, 1]*100
    } 
  
    if(TCL[i, 2] < 1 && is.na(TCL[i, 2])==FALSE){
       TCL[i, 2] <- TCL[i, 2]*100
    }
  
    if(TCL[i, 3] < 1 && is.na(TCL[i, 3])==FALSE){
       TCL[i, 3] <- TCL[i, 3]*100
    }
}

summary(TCL)
```
#### Both - v6 (TLC)
```{r echo=F}
TLC <- cbind(ver6[21], ver6[17], ver6[13])

for(i in 1:dim(TLC)[1]){
    if(TLC[i, 1] < 1 && is.na(TLC[i, 1])==FALSE){
       TLC[i, 1] <- TLC[i, 1]*100
    } 
  
    if(TLC[i, 2] < 1 && is.na(TLC[i, 2])==FALSE){
       TLC[i, 2] <- TLC[i, 2]*100
    }
  
    if(TLC[i, 3] < 1 && is.na(TLC[i, 3])==FALSE){
       TLC[i, 3] <- TLC[i, 3]*100
    }
}


summary(TLC)
```



# R
#### R - all
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,c(4:7, 10:13)], r2[,c(4:7, 10:13)], r3[,c(4:7, 14:17)], r4[,c(4:7, 18:21)], r5[,c(4:7, 14:17)], r6[,c(4:7, 18:21)])
log_y_scale_r <- rbind(r1[,c(4:7, 14:17)], r2[,c(4:7, 18:21)], r3[,c(4:7, 10:13)], r4[,c(4:7, 10:13)], r5[,c(4:7, 18:21)], r6[,c(4:7, 14:17)])
trnc_y_scale_r <- rbind(r1[,c(4:7, 18:21)], r2[,c(4:7, 14:17)], r3[,c(4:7, 18:21)], r4[,c(4:7, 14:17)], r5[,c(4:7, 10:13)], r6[,c(4:7, 10:13)])

con_4_r <- ctrl_y_scale_r[,4]
con_4_r[13] <- 12.5
con_4_r <- as.numeric(con_4_r)
for(i in 1:length(con_4_r)){
    if(con_4_r[i] < 1 && is.na(con_4_r[i])==FALSE){
       con_4_r[i] <- con_4_r[i]*100
    }
}

trn_4_r <- trnc_y_scale_r[,4]
for(i in 1:length(trn_4_r)){
    if(trn_4_r[i] < 1 && is.na(trn_4_r[i])==FALSE){
       trn_4_r[i] <- trn_4_r[i]*100
    }
}

log_4_r <- log_y_scale_r[,4]
log_4_r[13] <- 3
log_4_r <- as.numeric(log_4_r)
for(i in 1:length(log_4_r)){
    if(log_4_r[i] < 1 && is.na(log_4_r[i])==FALSE){
       log_4_r[i] <- log_4_r[i]*100
    }
}

y_scale_4_r <- cbind(con_4_r, log_4_r, trn_4_r)
summary(y_scale_4_r)
```



#### R - v1 (CLT)
```{r echo=F}
CLT <- cbind(r1[13], r1[17], r1[21])

for(i in 1:dim(CLT)[1]){
    if(CLT[i, 1] < 1 && is.na(CLT[i, 1])==FALSE){
       CLT[i, 1] <- CLT[i, 1]*100
    } 
  
    if(CLT[i, 2] < 1 && is.na(CLT[i, 2])==FALSE){
       CLT[i, 2] <- CLT[i, 2]*100
    }
  
    if(CLT[i, 3] < 1 && is.na(CLT[i, 3])==FALSE){
       CLT[i, 3] <- CLT[i, 3]*100
    }
}

summary(CLT)
```

#### R - v2 (CTL)
```{r echo=F}
CTL <- cbind(r2[13], r2[21], r2[17])
CTL$con_4[5] <- 12.5
CTL$log_4[5] <- 3

CTL$log_4 <- as.numeric(CTL$log_4)
CTL$con_4 <- as.numeric(CTL$con_4)

for(i in 1:dim(CTL)[1]){
    if(CTL[i, 1] < 1 && is.na(CTL[i, 1])==FALSE){
       CTL[i, 1] <- CTL[i, 1]*100
    } 
  
    if(CTL[i, 2] < 1 && is.na(CTL[i, 2])==FALSE){
       CTL[i, 2] <- CTL[i, 2]*100
    }
  
    if(CTL[i, 3] < 1 && is.na(CTL[i, 3])==FALSE){
       CTL[i, 3] <- CTL[i, 3]*100
    }
}


summary(CTL)
```
#### R - v3 (LCT)
```{r echo=F}
LCT <- cbind(r3[17], r3[13], r3[21])

for(i in 1:dim(LCT)[1]){
    if(LCT[i, 1] < 1 && is.na(LCT[i, 1])==FALSE){
       LCT[i, 1] <- LCT[i, 1]*100
    } 
  
    if(LCT[i, 2] < 1 && is.na(LCT[i, 2])==FALSE){
       LCT[i, 2] <- LCT[i, 2]*100
    }
  
    if(LCT[i, 3] < 1 && is.na(LCT[i, 3])==FALSE){
       LCT[i, 3] <- LCT[i, 3]*100
    }
}

summary(LCT)
```
#### R - v4 (LTC)
```{r echo=F}
LTC <- cbind(r4[21], r4[13], r4[17])

for(i in 1:dim(LTC)[1]){
    if(LTC[i, 1] < 1 && is.na(LTC[i, 1])==FALSE){
       LTC[i, 1] <- LTC[i, 1]*100
    } 
  
    if(LTC[i, 2] < 1 && is.na(LTC[i, 2])==FALSE){
       LTC[i, 2] <- LTC[i, 2]*100
    }
  
    if(LTC[i, 3] < 1 && is.na(LTC[i, 3])==FALSE){
       LTC[i, 3] <- LTC[i, 3]*100
    }
}

summary(LTC)
```
#### R - v5 (TCL)
```{r echo=F}
TCL <- cbind(r5[17], r5[21], r5[13])

for(i in 1:dim(TCL)[1]){
    if(TCL[i, 1] < 1 && is.na(TCL[i, 1])==FALSE){
       TCL[i, 1] <- TCL[i, 1]*100
    } 
  
    if(TCL[i, 2] < 1 && is.na(TCL[i, 2])==FALSE){
       TCL[i, 2] <- TCL[i, 2]*100
    }
  
    if(TCL[i, 3] < 1 && is.na(TCL[i, 3])==FALSE){
       TCL[i, 3] <- TCL[i, 3]*100
    }
}

summary(TCL)
```
#### R - v6 (TLC)
```{r echo=F}
TLC <- cbind(r6[21], r6[17], r6[13])

for(i in 1:dim(TLC)[1]){
    if(TLC[i, 1] < 1 && is.na(TLC[i, 1])==FALSE){
       TLC[i, 1] <- TLC[i, 1]*100
    } 
  
    if(TLC[i, 2] < 1 && is.na(TLC[i, 2])==FALSE){
       TLC[i, 2] <- TLC[i, 2]*100
    }
  
    if(TLC[i, 3] < 1 && is.na(TLC[i, 3])==FALSE){
       TLC[i, 3] <- TLC[i, 3]*100
    }
}


summary(TLC)

```


# Python
#### Python - all
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,c(4:7, 10:13)], py2[,c(4:7, 10:13)], py3[,c(4:7, 14:17)], py4[,c(4:7, 18:21)], py5[,c(4:7, 14:17)], py6[,c(4:7, 18:21)])
log_y_scale_py <- rbind(py1[,c(4:7, 14:17)], py2[,c(4:7, 18:21)], py3[,c(4:7, 10:13)], py4[,c(4:7, 10:13)], py5[,c(4:7, 18:21)], py6[,c(4:7, 14:17)])
trnc_y_scale_py <- rbind(py1[,c(4:7, 18:21)], py2[,c(4:7, 14:17)], py3[,c(4:7, 18:21)], py4[,c(4:7, 14:17)], py5[,c(4:7, 10:13)], py6[,c(4:7, 10:13)])

con_4_py <- ctrl_y_scale_py[,4]
for(i in 1:length(con_4_py)){
    if(con_4_py[i] < 1 && is.na(con_4_py[i])==FALSE){
       con_4_py[i] <- con_4_py[i]*100
    }
}

trn_4_py <- trnc_y_scale_py[,4]
for(i in 1:length(trn_4_py)){
    if(trn_4_py[i] < 1 && is.na(trn_4_py[i])==FALSE){
       trn_4_py[i] <- trn_4_py[i]*100
    }
}

log_4_py <- log_y_scale_py[,4]
for(i in 1:length(log_4_py)){
    if(log_4_py[i] < 1 && is.na(log_4_py[i])==FALSE){
       log_4_py[i] <- log_4_py[i]*100
    }
}

y_scale_4_py <- cbind(con_4_py, log_4_py, trn_4_py)
summary(y_scale_4_py)
```

#### Py - v1 (CLT)
```{r echo=F}
CLT <- cbind(py1[13], py1[17], py1[21])

for(i in 1:dim(CLT)[1]){
    if(CLT[i, 1] < 1 && is.na(CLT[i, 1])==FALSE){
       CLT[i, 1] <- CLT[i, 1]*100
    } 
  
    if(CLT[i, 2] < 1 && is.na(CLT[i, 2])==FALSE){
       CLT[i, 2] <- CLT[i, 2]*100
    }
  
    if(CLT[i, 3] < 1 && is.na(CLT[i, 3])==FALSE){
       CLT[i, 3] <- CLT[i, 3]*100
    }
}

summary(CLT)
```

#### Py - v2 (CTL)
```{r echo=F}
CTL <- cbind(py2[13], py2[21], py2[17])
CTL$con_4[5] <- 12.5
CTL$log_4[5] <- 3

CTL$log_4 <- as.numeric(CTL$log_4)
CTL$con_4 <- as.numeric(CTL$con_4)

for(i in 1:dim(CTL)[1]){
    if(CTL[i, 1] < 1 && is.na(CTL[i, 1])==FALSE){
       CTL[i, 1] <- CTL[i, 1]*100
    } 
  
    if(CTL[i, 2] < 1 && is.na(CTL[i, 2])==FALSE){
       CTL[i, 2] <- CTL[i, 2]*100
    }
  
    if(CTL[i, 3] < 1 && is.na(CTL[i, 3])==FALSE){
       CTL[i, 3] <- CTL[i, 3]*100
    }
}


summary(CTL)
```
#### Py - v3 (LCT)
```{r echo=F}
LCT <- cbind(py3[17], py3[13], py3[21])

for(i in 1:dim(LCT)[1]){
    if(LCT[i, 1] < 1 && is.na(LCT[i, 1])==FALSE){
       LCT[i, 1] <- LCT[i, 1]*100
    } 
  
    if(LCT[i, 2] < 1 && is.na(LCT[i, 2])==FALSE){
       LCT[i, 2] <- LCT[i, 2]*100
    }
  
    if(LCT[i, 3] < 1 && is.na(LCT[i, 3])==FALSE){
       LCT[i, 3] <- LCT[i, 3]*100
    }
}

summary(LCT)
```
#### Py - v4 (LTC)
```{r echo=F}
LTC <- cbind(py4[21], py4[13], py4[17])

for(i in 1:dim(LTC)[1]){
    if(LTC[i, 1] < 1 && is.na(LTC[i, 1])==FALSE){
       LTC[i, 1] <- LTC[i, 1]*100
    } 
  
    if(LTC[i, 2] < 1 && is.na(LTC[i, 2])==FALSE){
       LTC[i, 2] <- LTC[i, 2]*100
    }
  
    if(LTC[i, 3] < 1 && is.na(LTC[i, 3])==FALSE){
       LTC[i, 3] <- LTC[i, 3]*100
    }
}

summary(LTC)
```
#### Py - v5 (TCL)
```{r echo=F}
TCL <- cbind(py5[17], py5[21], py5[13])

for(i in 1:dim(TCL)[1]){
    if(TCL[i, 1] < 1 && is.na(TCL[i, 1])==FALSE){
       TCL[i, 1] <- TCL[i, 1]*100
    } 
  
    if(TCL[i, 2] < 1 && is.na(TCL[i, 2])==FALSE){
       TCL[i, 2] <- TCL[i, 2]*100
    }
  
    if(TCL[i, 3] < 1 && is.na(TCL[i, 3])==FALSE){
       TCL[i, 3] <- TCL[i, 3]*100
    }
}

summary(TCL)
```
#### Py - v6 (TLC)
```{r echo=F}
TLC <- cbind(py6[21], py6[17], py6[13])

for(i in 1:dim(TLC)[1]){
    if(TLC[i, 1] < 1 && is.na(TLC[i, 1])==FALSE){
       TLC[i, 1] <- TLC[i, 1]*100
    } 
  
    if(TLC[i, 2] < 1 && is.na(TLC[i, 2])==FALSE){
       TLC[i, 2] <- TLC[i, 2]*100
    }
  
    if(TLC[i, 3] < 1 && is.na(TLC[i, 3])==FALSE){
       TLC[i, 3] <- TLC[i, 3]*100
    }
}


summary(TLC)

```









