---
output:
  pdf_document:
    number_sections: true
fontsize: 11pt
documentclass: book
geometry: margin=0.8in
header-includes:
  \setlength{\parskip}{1em}
  \linespread {1.25}
  \usepackage{pdfpages}
  \usepackage{sectsty}
bibliography: bibliography.bib  
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, comment = NA, fig.pos = "!H", fig.width = 7, fig.height = 3)
library(knitr)
library(kableExtra)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
                      filename = 'render_toc.R')
```


\begin{titlepage}
    \begin{center}
        \vspace*{2cm}

        \textbf{An Emprirical Study of Data Visualisation}

        \vspace{0.5cm}
        \textit{An investigation into the theory behind data visualisation}

        \vspace{1.5cm}

        \textbf{Katie Murphy - 1632254}
        \textbf{Supervisor: Dr. Vincent Knight}
        \vspace{1.5cm}

        \includegraphics[width=0.5\textwidth]{universitylogo.eps}

        \vfill


        MMORS Final Year Dissertation for the Academic Year 2020-2021\\

        \vspace{0.5cm}
        Cardiff School of Mathematics

        \vspace{1.5cm}
        
        \textbf{Abtract}\\
        
        \textit{A study into the theory behind data visualisation, looking into different ways in which data can be
        interpreted visually to portray key information accurately in an elegant and concise manner using the
        libraries 'ggplot2' from R and 'matplotlib' from Python. The investigation will focus on aspects of
        visualisations that may either deliberately or accidentally mislead the observer, such as inapropriate axis 
        scalings and labeling, alteration of aspect ratios, and the use of colour. A survey is administered to gather
        quantitative information in regard to visual perception of visualisations with a variety of modifications and interviews with experienced programmers are held to gain an understanding on the
        opinions of the codes and visualisation packages themselves.}

    \end{center}
    

\end{titlepage}

\newpage

\section*{Acknowlegements}

I would like to thank my supervisor, Dr. Vincent Knight, for his invaluable support and encouragement throughout the last year. It has been a difficult year for many reasons, and Vince has always been highly understanding and supportive, and has helped me greatly in managing to get this dissertation to this point. I could not have managed without his continued input, support and guidance throughout.

I am also grateful for his patience in both teaching me and supporting in my own learning with regard to Git, VS Code and all the other background skills, and for always being willing to answer my many questions and help to fix any problems.

Finally, I would like to thank everyone who participated in the study, in both the survey and the interviews. Thank you to the interviewees for their time and very informative contributions to the study; Dr. Vincent Knight, Dr. Geraint Palmer, Dr.Nikoleta E. Glynatsi, Dr. Andreas Artemiou, Henry Wilde and Professor Owen Jones.

\section*{Computing Work}
This report was written and compiled using R Markdown [@Allaire2020-sr] with pdflatex and version control in Git [@git].

The R visualisations for the survey were created using R version 4.0.2 [@R] using `ggplot2` version 3.3.3 [@ggplot]. The Python visualisations were made using Python version 3.7.4 [@py] with `pyplot` from `matplotlib` version 3.3.3 [@matplot]. Additional packages and libraries used for visualisation include;

For R;
\begin{itemize}
   \item `dplyr` [@dplyr]
   \item `viridis` [@viridis]
   \item `cowplot` [@cowplot]
   \item `gridExtra` [@gridExtra]
   \item `kableExtra` [@kableExtra]
\end{itemize}

For Python;
\begin{itemize}
   \item `numpy` [@numpy]
   \item `pandas` [@pandas, @pandas2]
   \item `openpyxl` [@openpyxl]
   \item `math` [@math]
   \item `os` [@os]
\end{itemize}

R packages used for univariate analysis include;

\begin{itemize}
   \item `readxl` [@readxl]
   \item `dplyr` [@dplyr]
   \item `rstatix` [@rstatix]
   \item `BSDA` [@BSDA]
   \item `gridExtra` [@gridExtra]
   \item `knitr` [@knitr1, @knitr2, @knitr3]
   \item `kableExtra` [@kableExtra]
   \item `lawstat` [@lawstat]
   \item `cowplot` [@cowplot]
   \item `stringi` [@stringi]
\end{itemize}


\centering

\raggedright

\clearpage

\tableofcontents

\chapter{Introduction}

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/lit-review/main.rmd'}
```

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/survey/main.rmd'}
```

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/univariate-analysis/main.rmd'}
```

\chapter{Conclusion}

\chapter{Future Work}
Future work on this topic would include running focus groups with survey respondents to obtain more in depth information regarding the survey questions, for example asking open ended questions to understand the reasoning behind responses and to open a discussion about the topic in general. This is in addition to the prior mentioned topics for further research. If not for time constraints, JavaScript D3 would also have been implemented and investigated, and so this could perhaps be involved in a future study and compared to R and Python. An investigation into the combined D3/Python approach could also be studied.

Other potential interesting future research projects could include an exploration into the history of data visualisation, discussing very early visualisations such as that used by John Snow to investigate clusters of cases in the Broad Street cholera outbreak of 1854, eventually leading him to determine a particular water pump as the source of the outbreak, and the polar diagram created by Florence Nightingale, also in the 1850s, to explore causes of mortality in soldiers. Both of these figures, along with discussion, are presented in @grammar. It would be interesting to investigate these early visuals and discuss how they compare to, and have influenced, visualisation in the modern day.

#```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/appendix.rmd'}
#```

\chapter{References}
