---
output:
  pdf_document:
    number_sections: true
fontsize: 11pt
documentclass: book
geometry: margin=0.8in
header-includes:
  \setlength{\parskip}{1em}
  \linespread {1.25}
  \usepackage{pdfpages}
  \usepackage{sectsty}
bibliography: bibliography.bib  
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, comment = NA, fig.pos = "!H", fig.width = 7, fig.height = 3)
library(knitr)
library(kableExtra)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8", 
                      filename = 'render_toc.R')
```


\begin{titlepage}
    \begin{center}
        \vspace*{2cm}

        \textbf{An Emprirical Study of Data Visualisation}

        \vspace{0.5cm}
        \textit{An investigation into the theory behind data visualisation}

        \vspace{1.5cm}

        \textbf{Katie Murphy - 1632254}
        \vspace{1.5cm}

        \includegraphics[width=0.5\textwidth]{universitylogo.eps}

        \vfill


        MMORS Final Year Dissertation\\

        \vspace{0.5cm}
        Cardiff School of Mathematics

        \vspace{1.5cm}
        
        \textbf{Abtract}\\
        
        \textit{A study into the theory behind data visualisation, looking into different ways in which data can be
        interpreted visually to portray key information accurately in an elegant and concise manner using the
        libraries 'ggplot2' from R and 'matplotlib' from Python. The investigation will focus on aspects of
        visualisations that may either deliberately or accidentally mislead the observer, such as inapropriate axis 
        scalings and labeling, alteration of aspect ratios, and the use of colour. A survey is administered to gather
        quantitative information in regard to visual perception of visualisations with a variety of modifications and interviews with experienced programmers are held to gain an understanding on the
        opinions of the codes and visualisation packages themselves.}

    \end{center}
    

\end{titlepage}

\newpage

\section*{Acknowlegements}

I would like to thank my supervisor, Dr. Vince Knight, for his invaluable support and encouragement throughout the last year. It has been a difficult year for many reasons, and Vince has always been very understanding and supportive, and has helped me greatly in managing to get this dissertation to this point. I could not have managed without his continued support and guidance.

I also deeply appreciate his patience in teaching me and assisting in my own learning of Git and VS Code, and for always being willing to answer my many questions.

I would additionally like to thank Vince's children and pets for their lively contributions to meetings.

Finally, I would like to thank everyone who participated in the study, in both the survey and the interviews. Thank you to the interviewees for their time and very informative contributions to the study; Vince Knight, Geraint Palmer, Nikoleta E. Glynatsi, Andreas Artemiou, Henry Wilde and Owen Jones.

\vspace{5cm}

This report was written and compiled using R Markdown [@Allaire2020-sr] with pdflatex and version control using Git and GitHub [@git].


\centering

\raggedright

\clearpage

\tableofcontents

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/lit-review/main.rmd'}
```

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/survey/main.rmd'}
```

```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/chapters/univariate-analysis/main.rmd'}
```

\chapter{Conclusion}

\chapter{Future Work}
Future work on this topic would include running focus groups with survey respondents to obtain more in depth information regarding the survey questions, for example asking open ended questions to understand the reasoning behind responses and to open a discussion about the topic in general. This is in addition to the prior mentioned topics for further research. If not for time constraints, JavaScript D3 would also have been implemented and investigated, and so this could perhaps be involved in a future study and compared to R and Python. An investigation into the combined D3/Python approach could also be studied.

Other potential interesting future research projects could include an exploration into the history of data visualisation, discussing very early visualisations such as that used by John Snow to investigate clusters of cases in the Broad Street cholera outbreak of 1854, eventually leading him to determine a particular water pump as the source of the outbreak, and the polar diagram created by Florence Nightingale, also in the 1850s, to explore causes of mortality in soldiers. Both of these figures, along with discussion, are presented in @grammar. It would be interesting to investigate these early visuals and discuss how they compare to, and have influenced, visualisation in the modern day.

#```{r child = 'C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/markdown/appendix.rmd'}
#```

\chapter{References}
