---
title: "Univariate Analysis"
author: "Katie Murphy"
date: "27/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
rm(list=ls())
library(readxl)

for(i in 1:6){
    r <- assign(paste0("r",i), (as.data.frame(read_excel("C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/survey responses/raw.xlsx", paste0("R - v",i)))))
    py <- assign(paste0("py",i), (as.data.frame(read_excel("C:/Users/Katie/OneDrive/Uni_Work_Year4/Project/Year-4-Project/survey responses/raw.xlsx", paste0("Py - v",i)))))
    assign(paste0("ver",i), rbind(r, py))
}

ver1 <- ver1[-1,]
r1 <- r1[-1,]
py1 <- py1[-1,]

names(ver1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )

names(r1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )

names(py1) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
  
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "all_1", "all_2", "all_3",
  
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "sta_dge",
                 "a_cols_1", "a_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
  
                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )

names(r2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )

names(py2) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4",
                 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
                 
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "sta_dge",
                 "b_cols_1", "b_cols_2", 
  
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
  
                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )

names(r3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )

names(py3) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "con_1", "con_2", "con_3", "con_4", 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "wid_1", "wid_2", "wid_3",  
                 "all_1", "all_2", "all_3",
                 
                 "def_dge_1", "def_dge_2", "def_dge_3", "def_dge_4",
                 "def_sta_1", "def_sta_2", "def_sta_3", "def_sta_4", 
                 "sta_dge",
                 "c_cols_1", "c_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",                
  
                 "cd_zro",
                 "cd_trn"
                 )
###

names(ver4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )

names(r4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )

names(py4) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "log_1", "log_2", "log_3", "log_4",
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4", 
  
                 "nar_1", "nar_2", "nar_3", 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4",
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",  
                 "sta_dge",
                 "d_cols_1", "d_cols_2", 
  
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",

                 "cd_trn",
                 "cd_zro"
                 )
###

names(ver5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(r5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(py5) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "con_1", "con_2", "con_3", "con_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 
                 "wid_1", "wid_2", "wid_3",
                 "def_1", "def_2", "def_3", 
                 "nar_1", "nar_2", "nar_3", 
                 "all_1", "all_2", "all_3",
  
                 "vir_dge_1", "vir_dge_2", "vir_dge_3", "vir_dge_4",
                 "vir_sta_1", "vir_sta_2", "vir_sta_3", "vir_sta_4", 
                 "sta_dge",
                 "vir_cols_1", "vir_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "sep_1a", "sep_1b", "sep_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 
                 "cd_zro",
                 "cd_trn"
                 )
###

names(ver6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )
                 
names(r6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )

names(py6) <- c("timestamp", "consent", "age", "uni", "sp_aware", "obs_skl", "num_skl", "cblind", "vis_pro",
                 
                 "trn_1", "trn_2", "trn_3", "trn_4",
                 "log_1", "log_2", "log_3", "log_4", 
                 "con_1", "con_2", "con_3", "con_4",
                 
                 "wid_1", "wid_2", "wid_3",
                 "nar_1", "nar_2", "nar_3", 
                 "def_1", "def_2", "def_3", 
                 "all_1", "all_2", "all_3",
  
                 "gr_dge_1", "gr_dge_2", "gr_dge_3", "gr_dge_4",
                 "gr_sta_1", "gr_sta_2", "gr_sta_3", "gr_sta_4", 
                 "sta_dge",
                 "f_cols_1", "f_cols_2", 
  
                 "ab_zro_1", "ab_zro_1b", "ab_zro_2",
                 "ab_trn_1a", "ab_trn_1b", "ab_trn_2", 
                 "sep_1a", "sep_1b", "sep_2",
                 
                 "cd_zro",
                 "cd_trn"
                 )
### Y SCALES 
ctrl_y_scale <- rbind(ver1[,10:13], ver2[,10:13], ver3[,14:17], ver4[,18:21], ver5[,14:17], ver6[,18:21])
log_y_scale <- rbind(ver1[,14:17], ver2[,18:21], ver3[,10:13], ver4[,10:13], ver5[,18:21], ver6[,14:17])
trnc_y_scale <- rbind(ver1[,18:21], ver2[,14:17], ver3[,18:21], ver4[,14:17], ver5[,10:13], ver6[,10:13])
```
# Y scales

#### *Approximately many times would you say the 'Salmon Ladder' was used?*
#### Whole sample
```{r echo=F}
con_1_all <- ctrl_y_scale[,1]
con_1_all[26] <- 41.5 # take midpoint of two values
con_1_all <- as.numeric(con_1_all)

trn_1_all <- as.numeric(trnc_y_scale[,1])

log_1_all <- log_y_scale[,1]
log_1_all[c(23, 25, 67)] <- NA
log_1_all[35] <- 1e+15
log_1_all[54] <- 1e+9
log_1_all <- as.numeric(log_1_all)

y_scale_1_all <- cbind(con_1_all, trn_1_all, log_1_all)
summary(y_scale_1_all)
```

#### Python
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,10:13], py2[,10:13], py3[,14:17], py4[,18:21], py5[,14:17], py6[,18:21])
log_y_scale_py <- rbind(py1[,14:17], py2[,18:21], py3[,10:13], py4[,10:13], py5[,18:21], py6[,14:17])
trnc_y_scale_py <- rbind(py1[,18:21], py2[,14:17], py3[,18:21], py4[,14:17], py5[,10:13], py6[,10:13])

con_1_py <- ctrl_y_scale_py[,1]

trn_1_py <- as.numeric(trnc_y_scale_py[,1])

log_1_py <- log_y_scale_py[,1]
log_1_py[c(8, 10, 28)] <- NA
log_1_py[15] <- 1e+15
log_1_py[22] <- 1e+9
log_1_py <- as.numeric(log_1_py)

y_scale_py <- cbind(con_1_py, trn_1_py, log_1_py)
summary(y_scale_py)
```

#### R
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,10:13], r2[,10:13], r3[,14:17], r4[,18:21], r5[,14:17], r6[,18:21])
log_y_scale_r <- rbind(r1[,14:17], r2[,18:21], r3[,10:13], r4[,10:13], r5[,18:21], r6[,14:17])
trnc_y_scale_r <- rbind(r1[,18:21], r2[,14:17], r3[,18:21], r4[,14:17], r5[,10:13], r6[,10:13])

con_1_r <- ctrl_y_scale_r[,1]
con_1_r[15] <- 41.5 # take midpoint of two values
con_1_r <- as.numeric(con_1_r)

trn_1_r <- as.numeric(trnc_y_scale_r[,1])

log_1_r <- log_y_scale_r[,1]
log_1_r[c(8, 10, 28)] <- NA
log_1_r[15] <- 1e+15
log_1_r[22] <- 1e+9
log_1_r <- as.numeric(log_1_r)

y_scale_r <- cbind(con_1_r, trn_1_r, log_1_r)
summary(y_scale_r)
```

#### Order: CLT
```{r echo=F}
CLT <- cbind(ver1[10], ver1[14], ver1[18])
summary(CLT)
```
#### Order: CTL
```{r echo=F}
CTL <- cbind(ver2[10], ver2[18], ver2[14])
CTL[c(10, 12), 2] <- NA
CTL$log_1 <- as.numeric(CTL$log_1)
summary(CTL)
```
#### Order: LCT
```{r echo=F}
LCT <- cbind(ver3[14], ver3[10], ver3[18])
LCT[1, 1] <- 41.5
LCT[10, 2] <- 1e+15

LCT$con_1 <- as.numeric(LCT$con_1)
LCT$log_1 <- as.numeric(LCT$log_1)

summary(LCT)
```
#### Order: LTC
```{r echo=F}
LTC <- cbind(ver4[18], ver4[10], ver4[14])
summary(LTC)
```
#### Order: TCL
```{r echo=F}
TCL <- cbind(ver5[14], ver5[18], ver5[10])
TCL[8, 2] <- 1e+9
TCL$log_1 <- as.numeric(TCL$log_1)

summary(TCL)
```
#### Order: TLC
```{r echo=F}
TLC <- cbind(ver6[18], ver6[14], ver6[10])
summary(TLC)
```


#### *Approximately how much more than 'Log Grip' would you say 'Salmon Ladder' was was used?*
#### Whole sample
```{r echo=F}
con_2_all <- ctrl_y_scale[,2]
trn_2_all <- trnc_y_scale[,2]
log_2_all <- log_y_scale[,2]

y_scale_2_all <- cbind(con_2_all, trn_2_all, log_2_all)
summary(y_scale_2_all)
```

#### Python
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,10:13], py2[,10:13], py3[,14:17], py4[,18:21], py5[,14:17], py6[,18:21])
log_y_scale_py <- rbind(py1[,14:17], py2[,18:21], py3[,10:13], py4[,10:13], py5[,18:21], py6[,14:17])
trnc_y_scale_py <- rbind(py1[,18:21], py2[,14:17], py3[,18:21], py4[,14:17], py5[,10:13], py6[,10:13])

con_2_py <- ctrl_y_scale_py[,2]
trn_2_py <- trnc_y_scale_py[,2]
log_2_py <- log_y_scale_py[,2]

y_scale_2_py <- cbind(con_2_py, trn_2_py, log_2_py)
summary(y_scale_2_py)
```

#### R
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,10:13], r2[,10:13], r3[,14:17], r4[,18:21], r5[,14:17], r6[,18:21])
log_y_scale_r <- rbind(r1[,14:17], r2[,18:21], r3[,10:13], r4[,10:13], r5[,18:21], r6[,14:17])
trnc_y_scale_r <- rbind(r1[,18:21], r2[,14:17], r3[,18:21], r4[,14:17], r5[,10:13], r6[,10:13])

con_2_r <- ctrl_y_scale_r[,2]
trn_2_r <- trnc_y_scale_r[,2]
log_2_r <- log_y_scale_r[,2]

y_scale_2_r <- cbind(con_2_r, trn_2_r, log_2_r)
summary(y_scale_2_r)
```

#### Order: CLT
```{r echo=F}
CLT <- cbind(ver1[11], ver1[15], ver1[19])
summary(CLT)
```
#### Order: CTL
```{r echo=F}
CTL <- cbind(ver2[11], ver2[19], ver2[15])
summary(CTL)
```
#### Order: LCT
```{r echo=F}
LCT <- cbind(ver3[15], ver3[11], ver3[19])
summary(LCT)
```
#### Order: LTC
```{r echo=F}
LTC <- cbind(ver4[19], ver4[11], ver4[15])
summary(LTC)
```
#### Order: TCL
```{r echo=F}
TCL <- cbind(ver5[15], ver5[19], ver5[11])
summary(TCL)
```
#### Order: TLC
```{r echo=F}
TLC <- cbind(ver6[19], ver6[15], ver6[11])
summary(TLC)
```



#### *Approximately how much more than 'Quintuple Steps' would you say 'Salmon Ladder' was used?*
#### Whole sample
```{r echo=F}
con_3_all <- ctrl_y_scale[,3]
trn_3_all <- trnc_y_scale[,3]
log_3_all <- log_y_scale[,3]

y_scale_3_all <- cbind(con_3_all, trn_3_all, log_3_all)
summary(y_scale_3_all)
```

#### Python
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,10:13], py2[,10:13], py3[,14:17], py4[,18:21], py5[,14:17], py6[,18:21])
log_y_scale_py <- rbind(py1[,14:17], py2[,18:21], py3[,10:13], py4[,10:13], py5[,18:21], py6[,14:17])
trnc_y_scale_py <- rbind(py1[,18:21], py2[,14:17], py3[,18:21], py4[,14:17], py5[,10:13], py6[,10:13])

con_3_py <- ctrl_y_scale_py[,3]
trn_3_py <- trnc_y_scale_py[,3]
log_3_py <- log_y_scale_py[,3]

y_scale_3_py <- cbind(con_3_py, trn_3_py, log_3_py)
summary(y_scale_3_py)
```

#### R
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,10:13], r2[,10:13], r3[,14:17], r4[,18:21], r5[,14:17], r6[,18:21])
log_y_scale_r <- rbind(r1[,14:17], r2[,18:21], r3[,10:13], r4[,10:13], r5[,18:21], r6[,14:17])
trnc_y_scale_r <- rbind(r1[,18:21], r2[,14:17], r3[,18:21], r4[,14:17], r5[,10:13], r6[,10:13])

con_3_r <- ctrl_y_scale_r[,3]
trn_3_r <- trnc_y_scale_r[,3]
log_3_r <- log_y_scale_r[,3]

y_scale_3_r <- cbind(con_3_r, trn_3_r, log_3_r)
summary(y_scale_3_r)
```

#### Order: CLT
```{r echo=F}
CLT <- cbind(ver1[12], ver1[16], ver1[20])
summary(CLT)
```
#### Order: CTL
```{r echo=F}
CTL <- cbind(ver2[12], ver2[20], ver2[16])
summary(CTL)
```
#### Order: LCT
```{r echo=F}
LCT <- cbind(ver3[16], ver3[12], ver3[20])
summary(LCT)
```
#### Order: LTC
```{r echo=F}
LTC <- cbind(ver4[20], ver4[12], ver4[16])
summary(LTC)
```
#### Order: TCL
```{r echo=F}
TCL <- cbind(ver5[16], ver5[20], ver5[12])
summary(TCL)
```
#### Order: TLC
```{r echo=F}
TLC <- cbind(ver6[20], ver6[16], ver6[12])
summary(TLC)
```




In your opinion, approximately how many times would you say 'Log Grip' was used, as a percentage of the number of times 'Salmon Ladder' was used?


#### *In your opinion, approximately how many times would you say 'Log Grip' was used, as a percentage of the number of times 'Salmon Ladder' was used?*
#### Whole sample
```{r echo=F}
con_4_all <- ctrl_y_scale[,4]
con_4_all[18] <- 12.5
con_4_all <- as.numeric(con_4_all)
for(i in 1:length(con_4_all)){
    if(con_4_all[i] < 1 && is.na(con_4_all[i])==FALSE){
       con_4_all[i] <- con_4_all[i]*100
    }
}


trn_4_all <- trnc_y_scale[,4]
for(i in 1:length(trn_4_all)){
    if(trn_4_all[i] < 1 && is.na(trn_4_all[i])==FALSE){
       trn_4_all[i] <- trn_4_all[i]*100
    }
}

log_4_all <- log_y_scale[,4]
log_4_all[18] <- 3
log_4_all <- as.numeric(log_4_all)
trn_4_all <- trnc_y_scale[,4]
for(i in 1:length(log_4_all)){
    if(log_4_all[i] < 1 && is.na(log_4_all[i])==FALSE){
       log_4_all[i] <- log_4_all[i]*100
    }
}



y_scale_4_all <- cbind(con_4_all, trn_4_all, log_4_all)
summary(y_scale_4_all)

```

#### Python
```{r echo=F}

ctrl_y_scale_py <- rbind(py1[,10:13], py2[,10:13], py3[,14:17], py4[,18:21], py5[,14:17], py6[,18:21])
log_y_scale_py <- rbind(py1[,14:17], py2[,18:21], py3[,10:13], py4[,10:13], py5[,18:21], py6[,14:17])
trnc_y_scale_py <- rbind(py1[,18:21], py2[,14:17], py3[,18:21], py4[,14:17], py5[,10:13], py6[,10:13])

con_4_py <- ctrl_y_scale_py[,4]
for(i in 1:length(con_4_py)){
    if(con_4_py[i] < 1 && is.na(con_4_py[i])==FALSE){
       con_4_py[i] <- con_4_py[i]*100
    }
}

trn_4_py <- trnc_y_scale_py[,4]
for(i in 1:length(trn_4_py)){
    if(trn_4_py[i] < 1 && is.na(trn_4_py[i])==FALSE){
       trn_4_py[i] <- trn_4_py[i]*100
    }
}

log_4_py <- log_y_scale_py[,4]
for(i in 1:length(log_4_py)){
    if(log_4_py[i] < 1 && is.na(log_4_py[i])==FALSE){
       log_4_py[i] <- log_4_py[i]*100
    }
}

y_scale_4_py <- cbind(con_4_py, trn_4_py, log_4_py)
summary(y_scale_4_py)
```

#### R
```{r echo=F}

ctrl_y_scale_r <- rbind(r1[,10:13], r2[,10:13], r3[,14:17], r4[,18:21], r5[,14:17], r6[,18:21])
log_y_scale_r <- rbind(r1[,14:17], r2[,18:21], r3[,10:13], r4[,10:13], r5[,18:21], r6[,14:17])
trnc_y_scale_r <- rbind(r1[,18:21], r2[,14:17], r3[,18:21], r4[,14:17], r5[,10:13], r6[,10:13])

con_4_r <- ctrl_y_scale_r[,4]
con_4_r[13] <- 12.5
con_4_r <- as.numeric(con_4_r)
for(i in 1:length(con_4_r)){
    if(con_4_r[i] < 1 && is.na(con_4_r[i])==FALSE){
       con_4_r[i] <- con_4_r[i]*100
    }
}

trn_4_r <- trnc_y_scale_r[,4]
for(i in 1:length(trn_4_r)){
    if(trn_4_r[i] < 1 && is.na(trn_4_r[i])==FALSE){
       trn_4_r[i] <- trn_4_r[i]*100
    }
}

log_4_r <- log_y_scale_r[,4]
log_4_r[13] <- 3
log_4_r <- as.numeric(log_4_r)
for(i in 1:length(log_4_r)){
    if(log_4_r[i] < 1 && is.na(log_4_r[i])==FALSE){
       log_4_r[i] <- log_4_r[i]*100
    }
}

y_scale_4_r <- cbind(con_4_r, trn_4_r, log_4_r)
summary(y_scale_4_r)
```

#### Order: CLT
```{r echo=F}
CLT <- cbind(ver1[13], ver1[17], ver1[21])
summary(CLT)
```
#### Order: CTL
```{r echo=F}
CTL <- cbind(ver2[13], ver2[21], ver2[17])
summary(CTL)
```
#### Order: LCT
```{r echo=F}
LCT <- cbind(ver3[17], ver3[13], ver3[21])
summary(LCT)
```
#### Order: LTC
```{r echo=F}
LTC <- cbind(ver4[21], ver4[13], ver4[17])
summary(LTC)
```
#### Order: TCL
```{r echo=F}
TCL <- cbind(ver5[17], ver5[21], ver5[13])
summary(TCL)
```
#### Order: TLC
```{r echo=F}
TLC <- cbind(ver6[21], ver6[17], ver6[13])
summary(TLC)
```












